### 2022-06-13 Article.Rmd
13

---
title             : "The title"
shorttitle        : "Title"
author: 
  - name          : "Mari-Isabella Stan"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "University Alley, No.1"
    email         : "stanisabella@yahoo.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Ernst-August Doelle"
    affiliation   : "1"
    role:
      - "Writing - Review & Editing"
      - "Supervision"
  - name          : "Ernst-August Doelle"
    affiliation   : "1"
    role:
      - "Writing - Review & Editing"
      - "Supervision"
affiliation:
  - id            : "1"
    institution   : "Ovidius University of Constanța, România"
authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

>>>>

---
title             : "Study on the degree of transparency of the local public administration in Romania in a pandemic context"
shorttitle        : "Study on the degree of transparency of the local public administration in Romania in a pandemic context"
author: 
  - name          : "Mari-Isabella Stan"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "1"
    email         : "stanisabella@yahoo.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Cristian Opariuc-Dan"
    affiliation   : "1"
    role:
      - "Writing - Review & Editing"
      - "Supervision"
  - name          : "Tănase Tasențe"
    affiliation   : "1"
    role:
      - "Writing - Review & Editing"
      - "Supervision"
affiliation:
  - id            : "1"
    institution   : "Ovidius University of Constanța, Romania, Faculty of Law and Administrative Sciences"
authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
